---
title: "theCLE"
author: "Eden Williams" 
date: '2022-06-23'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

Here we have a bimodal plot. This means the graph has two peaks. The peaks are the same size which means the mean lies somewhere between 0 and 100. 



Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

 Here we have a trimodel plot because it has three peaks. All of the peaks are not the same size, with the one in the middle being the highest. For this plot the mean is 49.8 and the standard deviation is 29.3.
 
Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
print(mean(x.avg))
print(sd(x.avg))
```
Here we have a trimodal plot. The peaks are not all the same size. The mean is 50.5 and the standard deviation is 20.4.

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
print(mean(x.avg))
print(sd(x.avg))
```

Here we see the plot moving to being more unimodal. The mean is 50.6 and the standard deviation is 13.9.

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
print(mean(x.avg))
print(sd(x.avg))
```


Here the plot is unimodal because it only has one peak. The mean is 50.4 and the standard deviation is 10.6.



finally for 36 random samples.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
x.std<-apply(mdata,1, sd)
densityplot(x.avg,main="sample size 36")
print(mean(x.avg))
print(sd(x.avg))
```

The plot is unimodal, meaning it only has one peak. The mean is 50.1 and the standard deviation is 6.82.

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

For all the of the plots above the mean stayed at around 50. As far as the standard deviation, the more samples we had the small the standard deviation got. This is because each time we change the number of samples the standard deviation is divided by the square root of the number of samples. 





Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.